Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-13 paper.tex
Update affiliations
Update caption

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10]{Jared G. Galloway}
\author[11,12]{Ariella L. Gladstein}
\author[13]{Gregor Gorjanc}
\author[14]{Bing Guo}
\author[7]{Ben Jeffery}
\author[15]{Warren W. Kretzschmar}
\author[16]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[17]{Michael Matschiner}
\author[16]{Dominic Nelson}
\author[18]{Nathaniel S. Pope}
\author[19]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[20]{Kumar Saunack}
\author[21]{Thibaut Sellinger}
\author[22]{Kevin Thornton}
\author[23]{Hugo van Kemenade}
\author[7]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[15,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[24,$\dagger$]{Jere Koskela}
\author[10,25,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[12]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[13]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[14]{Institute for Genome Sciences, University of Maryland School of
Medicine, Baltimore, MD}
% Winni
\affil[15]{Center for Hematology and Regenerative Medicine, Karolinska Institute}
% Simon, Dom, Ivan
\affil[16]{Department of Human Genetics, McGill University}
% Michael
\affil[17]{Natural History Museum, University of Oslo}
% Nathaniel
\affil[18]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[19]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[20]{IIT Bombay, India}
% Thibaut
\affil[21]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[22]{Ecology and Evolutionary Biology, University of California Irvine}
% Hugo
\affil[23]{FIXME HUGO's AFFILIATION}
% Jere
\affil[24]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[25]{Department of Mathematics, University of Oregon}

@@

\begin{figure}
    \includegraphics{illustrations/mutated_tree}
    \caption{
        \label{fig-mutated-trees}
        Visualisation of the separation between ancestry and mutation
        simulation. (A) The result of an invocation of \texttt{sim\_ancestry}
        is two trees along a 1kb chunk of genome relating two diploid samples.
        (B) This ancestry is provided as the input to \texttt{sim\_mutations},
        which adds mutations.
        Graphics produced using \tskit's \texttt{draw\_svg} method.
    }
\end{figure}

>>>>

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10]{Jared G. Galloway}
\author[11,12]{Ariella L. Gladstein}
\author[13]{Gregor Gorjanc}
\author[14]{Bing Guo}
\author[7]{Ben Jeffery}
\author[15]{Warren W. Kretzschmar}
\author[16]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[17]{Michael Matschiner}
\author[16]{Dominic Nelson}
\author[18]{Nathaniel S. Pope}
\author[19]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[20]{Kumar Saunack}
\author[21]{Thibaut Sellinger}
\author[22]{Kevin Thornton}
\author[9]{Hugo van Kemenade}
\author[7]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[15,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[23,$\dagger$]{Jere Koskela}
\author[10,24,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo, Hugo
\affil[9]{No affiliation}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[12]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[13]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[14]{Institute for Genome Sciences, University of Maryland School of
Medicine, Baltimore, MD}
% Winni
\affil[15]{Center for Hematology and Regenerative Medicine, Karolinska Institute}
% Simon, Dom, Ivan
\affil[16]{Department of Human Genetics, McGill University}
% Michael
\affil[17]{Natural History Museum, University of Oslo}
% Nathaniel
\affil[18]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[19]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[20]{IIT Bombay, India}
% Thibaut
\affil[21]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[22]{Ecology and Evolutionary Biology, University of California Irvine}
% Jere
\affil[23]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[24]{Department of Mathematics, University of Oregon}

@@

\begin{figure}
    \includegraphics{illustrations/mutated_tree}
    \caption{
        \label{fig-mutated-trees}
        Visualisation of the separation between ancestry and mutation
        simulation. (A) The result of an invocation of \texttt{sim\_ancestry}
        is two trees along a 1kb chunk of genome relating three diploid samples.
        Each diploid individual consists of two genomes (or nodes), indicated
        by colour.
        (B) This ancestry is provided as the input to \texttt{sim\_mutations},
        which adds mutations.
        Graphics produced using \tskit's \texttt{draw\_svg} method.
    }
\end{figure}
